
---
title: "Final Project: Analysis of Baseball Hits"
author: "Keaton Gull, Spencer Miller"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

### Background/Purpose

This project analyzes baseball player performance using a dataset of player statistics. Specifically, we investigate player hits in relation to other variables such as team, position, and at-bats. Understanding these relationships can help scouts and managers make more data-driven decisions.

### Research Questions
The study will address the following research questions using different inferential statistical methods:
1. Is there a significant difference in the mean number of hits between teams with a winning record (above 50%) and teams with a losing record (below 50%)?
2. Is the average batting average of American League (AL) teams significantly greater than the overall league-wide average?
  


## Methodology

### Data Description

```{r}

```

### Data Analysis Plan



### Hypotheses

- **t-test**  


- **z-test**  


- **Chi-square**  


- **Regression**  


## Results

### Descriptive Statistics

```{r}

```

### t-test

```{r}

```

### z-test for Proportions

```{r}

```

### Chi-square Test

```{r}

```

### Regression Analysis

```{r}

```

## Discussion

### Interpretation of Results


### Limitations



