
---
title: "Final Project: Analysis of Baseball Hits"
author: "Keaton Gull, Spencer Miller"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

### Background/Purpose

This project analyzes baseball player performance using a dataset of player statistics. Specifically, we investigate player hits in relation to other variables such as team, position, and at-bats. Understanding these relationships can help scouts and managers make more data-driven decisions.

### Research Questions
The study will address the following research questions using different inferential statistical methods:<br>
1. Is there a significant difference in the mean number of hits/game between teams with a winning record (above 50%) and teams with a losing record (below 50%)?<br>
2. Does the proportion of hits to runs for NL league vary significantly from that of the AL league?
  


## Methodology

### Data Description
The Dataset "Baseball Hits" was collected from Wiley eTextbook datasets. The data set consists of the following variables:

- **Team and League**: ARI(NL), ATL(NL), BAL(AL), BOS(AL), etc.
- **Team Stats**:
    - Wins (out of 162)
    - Runs (Total)
    - Hits (Total)
    - Doubles (Total)
    - Triples (Total)
    - Home Runs (Total)
    - RBI (Total)
    - Stolen Bases (Total)
    - Caught Stealing (Total)
    - Walks (Total)
    - Strikeouts (Total)
    - Batting Average (Average)


### Data Analysis Plan



```{r}
library(dplyr)
library(ggplot2)
BBH = read.csv('BaseballHits.csv')
str(BBH)
```


### Hypotheses
- The teams with a winning season (above 50%) have a much higher average number of hits/game compared to teams with a losing season (below 50%).

```{r}
BBH$Hits_per_Game <- BBH$Hits / 162  # Calculate Hits per Game
BBH$Winning_Record <- ifelse(BBH$Wins > 81, "Winning", "Losing")  # Winning Record

# data = data.frame(Hits_per_game, Winning_Record)

# Group by Winning_Record and summarize Mean for Winning and Losing
summary_stats <- BBH %>%
  group_by(Winning_Record) %>%
  summarise(
    Mean_Hits = mean(Hits_per_Game),
    SD_Hits = sd(Hits_per_Game),
    Count = n()
  )

summary_stats

# print(data)

boxplot(Hits_per_Game ~ Winning_Record, data=BBH)

t.test(Hits_per_Game ~ Winning_Record, alternative="greater", conf.level=0.95, data=BBH)
```

### Hypotheses
- The National League (NL) teams have a significantly different proportion of hits to runs compared to the American League (AL) teams.

```{r}
AL_Teams = BBH %>% filter(League == "AL")
NL_Teams = BBH %>% filter(League == "NL")

NL_Hit_Total = sum(NL_Teams$Hits)
NL_Run_Total = sum(NL_Teams$Runs)
NL_Hit_Run_Prop = NL_Run_Total/NL_Hit_Total

print(NL_Hit_Total)
print(NL_Run_Total)

AL_Hit_Total = sum(AL_Teams$Hits)
AL_Run_Total = sum(AL_Teams$Runs)
AL_Hit_Run_Prop = AL_Run_Total/AL_Hit_Total

print(AL_Hit_Total)
print(AL_Run_Total)

# Create a data frame to display the results
hit_run_prop_df <- data.frame(
  League = c("NL", "AL"),
  Hit_to_Run_Proportion = c(NL_Hit_Run_Prop, AL_Hit_Run_Prop)
)

# Print the data frame
print(hit_run_prop_df)

ggplot(hit_run_prop_df, aes(x=League, y=Hit_to_Run_Proportion, fill = League)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Proportion of Hits To Runs Between AL and NL",
       x = "League",
       y = "Hit to Run Proportion") +
  theme_minimal()

prop.test(x=c(AL_Run_Total, NL_Run_Total), n=c(AL_Hit_Total, NL_Hit_Total), correct = FALSE)
```

### Hypotheses


- **Chi-square**  

### Hypotheses


- **Regression**  


## Results

### Descriptive Statistics

```{r}

```

### t-test

```{r}

```

### z-test for Proportions

```{r}

```

### Chi-square Test

```{r}

```

### Regression Analysis

```{r}

```

## Discussion

### Interpretation of Results


### Limitations



