
---
title: "Final Project: Analysis of Baseball Hits"
author: "Keaton Gull, Spencer Miller"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

### Background/Purpose

This project analyzes baseball player performance using a dataset of player statistics. Specifically, we investigate player hits in relation to other variables such as team, position, and at-bats. Understanding these relationships can help scouts and managers make more data-driven decisions.

### Research Questions
The study will address the following research questions using different inferential statistical methods:<br>
1. Is there a significant difference in the mean number of hits/game between teams with a winning record (above 50%) and teams with a losing record (below 50%)?<br>
2. Is the average batting average of American League (AL) teams significantly greater than the overall league-wide average?
  


## Methodology

### Data Description
The Dataset "Baseball Hits" was collected from Wiley eTextbook datasets. The data set consists of the following variables:

- **Team and League**: ARI(NL), ATL(NL), BAL(AL), BOS(AL), etc.
- **Team Stats**:
    - Wins (out of 162)
    - Runs (Total)
    - Hits (Total)
    - Doubles (Total)
    - Triples (Total)
    - Home Runs (Total)
    - RBI (Total)
    - Stolen Bases (Total)
    - Caught Stealing (Total)
    - Walks (Total)
    - Strikeouts (Total)
    - Batting Average (Average)


### Data Analysis Plan



```{r}
library(dplyr)
library(ggplot2)
BBH = read.csv('BaseballHits.csv')
str(BBH)
```


### Hypotheses
- The teams with a winning season (above 50%) have a much higher average number of hits/game compared to teams with a losing season (below 50%).

```{r}
library(dplyr)

BBH$Hits_per_Game <- BBH$Hits / 162  # Calculate Hits per Game
BBH$Winning_Record <- ifelse(BBH$Wins > 81, "Winning", "Losing")  # Winning Record

# data = data.frame(Hits_per_game, Winning_Record)

# Group by Winning_Record and summarize Mean for Winning and Losing
summary_stats <- BBH %>%
  group_by(Winning_Record) %>%
  summarise(
    Mean_Hits = mean(Hits_per_Game),
    SD_Hits = sd(Hits_per_Game),
    Count = n()
  )

summary_stats

# print(data)

boxplot(Hits_per_Game ~ Winning_Record, data=BBH)

t.test(Hits_per_Game ~ Winning_Record, alternative="greater", conf.level=0.95, data=BBH)
```

### Hypotheses


- **z-test**

### Hypotheses


- **Chi-square**  

### Hypotheses


- **Regression**  


## Results

### Descriptive Statistics

```{r}

```

### t-test

```{r}

```

### z-test for Proportions

```{r}

```

### Chi-square Test

```{r}

```

### Regression Analysis

```{r}

```

## Discussion

### Interpretation of Results


### Limitations



